Follow the Flow of Rain and Paint: \break An Output Sensitive Contour Tree Algorithm

### 2014-09-18 paint-contour-tree.tex
more changes

\begin{lemma} \label{lem:light} $\sum_{p \in \cL} \sum_{v \in p} \log |H_v| = O(\sum_{p \in \cL'} |H_p| \log |H_p|)$.
\end{lemma}

@@

\begin{proof} (of \Thm{runtime}) We split into heavy and light paths.
We have $\sum_{v \in T} \log |H_v| =$  $\sum_{p \in \cL} \sum_{v \in p} \log |H_v| + $ $\sum_{p \in \cH} \sum_{v \in p} \log |H_v|$.
For the first term, we apply \Lem{light} to bound by $O(\sum_{p \in \cL'} |H_p| \log |H_p|)$.
Then we apply \Clm{above} to bound by $O(\sum_{p \in \cH} |p|\log |p|)$.
The latter is also bounded by the same expression, by \Lem{pathBounds}. By definition,
$\sum_{p \in \cH} |p|\log |p| \leq \cost(\pmax(T))$.
\end{proof}

@@

\subsection{Proving \Lem{light}}

We can simplify a little. We split the summation and apply \Lem{pathBounds}. Finally,
we note that for $p \in \cL$, $|p| \leq |H_p|$.
\begin{eqnarray*} 
\sum_{p \in \cL} \sum_{v \in p} \log |H_v| & = & \sum_{p \in \cL'} \sum_{v \in p} \log |H_v| + \sum_{p \in \cL \setminus \cL'} \sum_{v \in p} \log |H_v| \\
& = & \sum_{p \in \cL \setminus \cL'} \sum_{v \in p} \log |H_v| + O(|p|\log |H_p|) = \sum_{p \in \cL \setminus \cL'} \sum_{v \in p} \log |H_v| + O(|H_p|\log |H_p|)
\end{eqnarray*}

@@

>>>>

\begin{lemma} \label{lem:light} For the path decomposition $\pmax(T)$, $\sum_{p \in \cL} \sum_{v \in p} \log |H_v| = O(\sum_{p \in \cL'} |H_p| \log |H_p|)$.
\end{lemma}

@@

\begin{proof} (of \Thm{runtime}) We focus on $\pmax(T)$ and split into heavy and light paths.
We have $\sum_{v \in T} \log |H_v| =$  $\sum_{p \in \cL} \sum_{v \in p} \log |H_v| + $ $\sum_{p \in \cH} \sum_{v \in p} \log |H_v|$.
For the first term, we apply \Lem{light} to bound by $O(\sum_{p \in \cL'} |H_p| \log |H_p|)$.
Then we apply \Clm{above} to bound by $O(\sum_{p \in \cH} |p|\log |p|)$.
The latter is also bounded by the same expression, by \Lem{pathBounds}. By definition,
$\sum_{p \in \cH} |p|\log |p| \leq \cost(\pmax(T))$.
\end{proof}

@@

\subsection{Proving \Lem{light}} \label{sec:light}

Our focus is on $\pmax(T)$.
We can simplify a little. We split the summation and apply \Lem{pathBounds}. Finally,
we note that for $p \in \cL$, $|p| \leq |H_p|$.
\begin{eqnarray*} 
\sum_{p \in \cL} \sum_{v \in p} \log |H_v| & = & \sum_{p \in \cL \setminus \cL'} \sum_{v \in p} \log |H_v| + \sum_{p \in \cL'} \sum_{v \in p} \log |H_v|\\
& = & \sum_{p \in \cL \setminus \cL'} \sum_{v \in p} \log |H_v| + O(\sum_{p \in \cL'} |p|\log |H_p|) = \sum_{p \in \cL \setminus \cL'} \sum_{v \in p} \log |H_v| + O(\sum_{p \in \cL'} |H_p|\log |H_p|)
\end{eqnarray*}

@@

It suffices to focus on unsupported light paths. \Lem{light} can be reduced to the following.

\begin{lemma} \label{lem:support} $\sum_{p \in \cL \setminus \cL'} \sum_{v \in p} \log |H_v| = O(\sum_{p \in \cL'} |H_p| \log |H_p|)$.
\end{lemma}

We now construct the shrub of unsupported light paths $\cU$. Consider $p \in \cL \setminus \cL'$,
and traverse the chain of ancestors
